Part III

### 2021-06-19 algebra.tex
added 1d holomorphic motivation

Suppose now that $G$ is a complex Lie group and it acts on the symplectic complex vector space $V$ by holomorphic symplectomorphisms.
Then $G$ also acts on the algebraic loop space $V[z,z^{-1}]$ as a ``global'' symmetry:
the action is independent of $z$.
On the other hand, if we consider the infinitesimal action $\fg \to {\rm SympVect}(V)$,
there is, in fact, a natural extension to a ``local'' symmetry $\fg[z,z^{-1}] \to {\rm SympVect}(V[z,z^{-1}])$.
Geometrically, we let a $\fg$-valued function $x(z)$ act pointwise on the algebraic loop space.

>>>>

Suppose now that $G$ is a complex Lie group and it acts on the symplectic complex vector space $V$ by holomorphic symplectomorphisms.
Then $G$ also acts on the algebraic loop space $V[z,z^{-1}]$ and also on formal loops $V((z))$ as a ``global'' symmetry:
the action is independent of $z$.
On the other hand, if we consider the infinitesimal action $\fg \to {\rm SympVect}(V)$,
there is, in fact, a natural extension to a ``local'' symmetry $\fg[z,z^{-1}] \to {\rm SympVect}(V((z)))$.
Geometrically, we let a $\fg$-valued function $x(z)$ act pointwise (on the formal disk) on the formal loop space.

\owen{OK, my plan is to say that there is an obstruction to lifting the moment map to a quantum moment map, leading to the central extension.}
